A comparison of single-cell trajectory inference methods

### 2021-10-28 manuscript/paper.Rmd
update manuscript render

*`r format(Sys.time(), '%d %B, %Y')`*

Commit: `r print_url(paste0("https://www.github.com/dynverse/dynbenchmark/tree/", git2r::revparse_single(".","HEAD")$sha))`
```{r}
n_tools <- nrow(tools)
n_tools_evaluated <- nrow(filter(tools, evaluated))
n_methods_evaluated <- nrow(filter(methods, evaluated, source == "tool"))
n_control_methods_evaluated <- nrow(filter(methods, evaluated, source == "control"))
n_datasets_real <- nrow(list_datasets("real"))
n_datasets_synthetic <- nrow(list_datasets("synthetic"))
```
# Abstract

@@

```{r}
methods_evaluated <- load_methods()
special_methods <- c("mfa", "dpt", "slice", "sincell", "calista", "urd")
# create functions to list the methods within a particular conversion category
list_wrapper_type_methods <- function(wrapper_types_oi) {
  methods_evaluated %>% 
    filter(wrapper_type %in% wrapper_types_oi) %>% 
    mutate(name = paste0(name, ifelse(id %in% special_methods, "\\*", ""))) %>% 
    pull(name) %>% 
    sort() %>%
    label_vector()
}
```

>>>>

Published in Nat Biotechnol 37, 547–554 (2019). doi: [10.1038/s41587-019-0071-9](https://doi.org/10.1038/s41587-019-0071-9).

```{r}
n_tools <- nrow(tools)
n_tools_evaluated <- nrow(filter(tools, method_evaluated))
n_methods_evaluated <- nrow(filter(methods, method_evaluated, method_source == "tool"))
n_control_methods_evaluated <- nrow(filter(methods, method_evaluated, method_source == "control"))
n_datasets_real <- nrow(list_datasets("real"))
n_datasets_synthetic <- nrow(list_datasets("synthetic"))
```
# Abstract

@@

```{r}
methods_evaluated <- load_methods()
special_methods <- c("mfa", "dpt", "slice", "sincell", "calista", "urd")
# create functions to list the methods within a particular conversion category
list_wrapper_type_methods <- function(wrapper_types_oi) {
  methods_evaluated %>% 
    filter(wrapper_type %in% wrapper_types_oi) %>% 
    mutate(name = paste0(method_name, ifelse(method_id %in% special_methods, "\\*", ""))) %>% 
    pull(name) %>% 
    sort() %>%
    label_vector()
}
```
